\chapter{Company description} \label{description}
We are 4 young and motivated people who have founded a start-up called SkyPulse Technologies. SkyPulse Technologies is a Public limited company. With this newly founded company, we have set ourselves the goal of speeding up and optimizing the transport of medicinal samples. This new time-optimized transport makes it possible to help patients better and improve collaboration between laboratories and hospitals. This transportation is achieved with our drones, which are controlled with artificial intelligence. These drones fly their routes between hospitals and laboratories and transport the respective samples.
\newline
Our target market is therefore the pharmaceutical industry, and more specifically hospitals and laboratories.
\newline
Our start-up is divided into two different sectors. There is a technical department and a commercial department. The technical department is further divided into three different subdivisions:
\begin{itemize}
  \item Research and development
  \item Planning and operational organization
  \item Production
\end{itemize}
The commercial department is also divided into three different subdivisions:
\begin{itemize}
  \item Finance and accounting
  \item Administration
  \item Distribution
\end{itemize}
We have divided up the various departments according to our interests. Céline and Fabian are responsible for the Research and development department. Xenia is responsible for the Planning and operational organization and also for the production. Jonas is responsible for the commercial department and all corresponding subdivisions.