\chapter{Ownership} \label{ownership}
Our main objective is to help patients. For this goal we created our drones which are controlled by Artificial Intelligence. They are programmed to fly their corresponding route. These drones can transport medicine or medicinal samples. With these drones we can make the collaboration more time-efficient. Therefore problems as long delivery times with organ donating and urgent samples can be eliminated. Because for the patients, every minute counts. The drones can transport up to 5kg each. It is also possible to transport critical samples such as organs, which have to be stored under special conditions. We offer the appropriate transportation for each sample required and thus guarantee that the samples reach their destination in the highest quality. However, in order to guarantee the highest possible quality of the samples, it should be noted that the transportation of the drones is dependent on the weather. If the weather is too bad (strong winds, thunderstorms), the drones cannot fly, as the samples and therefore their corresponding quality would be at risk. For the transportation times, the samples are divided into three different categories:
\begin{itemize}
  \item Very urgent
  \item urgent
  \item not urgent
\end{itemize}
Customers can specify how urgent their sample is and in what time frame the sample should be delivered. The customer must therefore provide all important information about the sample so that it can be dealt with individually.
\newline
\newline
For our locations, we focus on a small set of either large, economically strong cities, cities with a strong pharma presence or cities in dire need of this technology. The set of cities includes the following:
\begin{itemize}
  \item Basel
  \item Vienna
  \item London
  \item Paris
  \item Madrid
  \item Barcelona
  \item Berlin
  \item Kiev
\end{itemize}
We chose these locations because we need to validate our product/service idea on focused markets that resemble ones where the finished product is deployed in. Rural areas or small cities are also important, but not the key market of this company. A nationwide or even continent/worldwide expansion is not in the scope of a startup and can be achieved once our idea has been validated in different cities. Therefore large cities that are economically stable and have a strong pharma presence are the easiest to target in the beginning. There we will be able to test our drones and optimize them accordingly.
\newline
\newline
In order to know all possible contact points with our customers, we have integrated a representative from a laboratory and a representative from a hospital into our start-up.
\newline
\newline
For the representative of the laboratory we chose Jona Müller, he is a 32 year old chemical laboratory technician who works at Viollier. He aims to lead a major research project in pharmaceutical analysis. Jona Müller represents a dedicated and skilled professional, deeply involved in the pharmaceutical industry's innovative and dynamic nature, and an ideal customer for a drone delivery service catering to laboratory needs.
\newline
\newline
For the representative of the hospital we chose Dr. Sarah Becker. She is a 38 year old oncologist who works at a cantonal hospital. She aims to contribute to groundbreaking research in targeted cancer therapies. Interested in developing supportive care programs for cancer survivors Dr. Sarah Becker represents a compassionate and innovative medical professional, dedicated to advancing cancer treatment and care. Her reliance on the drone delivery service highlights its importance in providing timely and critical medical supplies in the field of oncology.