\chapter{Outlook} \label{outlook}
For our future outlook, the first thing we have to do is to evaluate our current data. We will have to gather some qualitative and quantitative data about the business finances, operations, products or services, customers, and employees. With this newly acquired information, we can find out where our strengths and weaknesses are. It's really important to know soon enough what works in our business and what doesn't. We will talk to our current customers and ask them about their opinions about the drones and the service. Ideally, with a survey we will find out, how we can optimize our drones and how we can improve the service and communication between our customers and us. In the future, we want to expand our offerings. Through the information we gathered, we can optimize our drones and the service. When the drones established themselves in the planned cities and everything works out as it was predicted, we also intend to expand our business to different places. If the circumstances allow it, our concept could also be established in smaller and poorer cities. For this we would have to adjust our prices for the drones, because poorer cities can't afford to pay as much as big, pharma oriented cities. A possibility would also be to create a new kind of drone, which is able to transport heavier load. With this we could transport a larger variety of samples and also more samples in one transport. This leads to more efficiency and a greater variety of our service.
\newline
Before we offer new services or a new kind of drone, we will have to do some further market research. We will have to find out what is popular on the market and where the gaps in the market are. Drone transportation is a relatively new market concept, so theoretically there are still many options open to us. Of course, you have to bear in mind that there could be new competitors in this market at any time which offer a similar service to us. However, our aim is to remain in the pharmaceutical industry and the health sector to focus on the transportation of medical samples. With this specific focus, we want to dominate the drone transportation market by guaranteeing the highest possible transport quality.
\newline
An important fact for the future of our business are also the finances. We also have to take a closer look at the income and expenditure. In order to provide our service in poorer cities, we will have to optimize our income and expenses. By optimizing the expenses for our business, we will be able to save more money. By minimizing the production costs of the drones, we could save the most money. The best way to save on production costs is to look at where the production would be the cheapest in relation to quality. The quality of the drones is our top priority, so we won't produce them with any cheap material. This is because poor quality drones could endanger the transport of critical samples. In order to continue financing our business, we will also be looking for further investors. To achieve this, we will expand our network and spread our ideas further. The most suitable partners would of course be large pharmaceutical companies or hospitals that show interest in our service and would like to be a part of it. This could also improve future cooperation between the two industries. If we expand our business, we will also have to hire new employees in order to guarantee the best possible service.
\newline
With all these mentioned factors, we will be able to grow and expand our business. We hope that this type of transport will become established worldwide in the future and that it will speed up the transportation of medical samples, which could save many patient's lives. We look forward to being a part of it.
